Elicitation Complexity via Convex Piecewise Linear Loss Functions

### 2018-10-07 jessie-writeup/jessie-writeup.tex
notes on jessie writeup

The set $\Theta \subseteq 2^{\Delta(\Y)}$ is an unlabeled property, and finite if $|\Theta| < \infty$.
Observe that $\Theta$ is a set of level sets that divide the simplex, and not a function.

\begin{definition}
Let $\Gamma$ be a labeled property.
Define $\text{strip}(\Gamma) := \{ \Gamma_r : r \in \R \}$.
Informally, strip removes labels from the property.
\jessie{Note: Strip includes the boundaries of level sets / lower dimensional level sets.}
\end{definition}

@@

\begin{notation}
  Consider two labeled properties $\Gamma' : \P \toto \R$ and $\Gamma : \P \toto \R$.
  We say $\Gamma' \leq \Gamma$ if removing reports from $\Gamma$ yields $\Gamma'$.
  (i.e. $\Gamma' = \R' \cap \Gamma$ for some $\R' \subseteq \R$)
\end{notation}

@@

\begin{definition}\label{def:unlabeled-nonredundant}
  An elicitable, unlabeled property $\Theta$ is \emph{nonredundant} if for any full dimensional $\theta_1, \theta_2 \in \Theta$ we observe $\theta_1 \cap \theta_2 = \emptyset$ almost everywhere.
  \jessie{Should be equivalent to definition of nonredundancy for labeled property $\Gamma$, shown in Lemma~\ref{lem:nonredundant-defs-equivalent}.}
\end{definition}

Other notes before starting:
\begin{itemize}
\item (Assuming the metric space is $(\Delta(\Y), \rho)$, where $\rho$ is Euclidean distance, although I don't think the choice of metric matters?).
We just use this looking at interiors of level sets.
\item Using generalized Lebesgue measure on $\P \subset \reals^{|\Delta(\Y)|-1}$
\item The interior of a level set $X_r$ is defined as $\inter{X_r} = \{p \in X_r: \epsilon > 0,  \forall q \in B(\epsilon,p), r \in \argmin_r \E_q L(r,Y)\}$
\item Define the boundary of the closed set $X$ by $bd(X) := X \setminus \inter{X}$.
\item A level set $\theta$ is \emph{full-dimensional} if $dim(\aff(\theta)) = dim(P)$. 
Equivalently, $\theta$ is full-dimensional if there are distributions $p_1, p_2, \ldots, p_n \in \theta$ so that $p_1, \ldots, p_n$ are affinely independent.
\item A full-dimensional level set has non-empty interior.
\end{itemize}

@@

\begin{conjecture}\label{conj:gam-prime-exists}
	Let $\Gamma$ be a nondegenerate elicitable property with a finite set of \jessie{full-dimensional} level sets \jessie{$\Theta$ so that $\bigcup_{\theta \in \Theta}\theta = \P$}.
	There exists a nondegenerate, nonredundant property $\Gamma'$ such that $\Gamma' \leq \Gamma$. 
\end{conjecture}
\begin{proof}
\emph{Assumptions used: Finite level sets, elicitability implies convex BR, i.e. differentiable a.e.}

>>>>

A set $\Theta \subseteq 2^{\Delta(\Y)}$ is an unlabeled property, and finite if $|\Theta| < \infty$.
Observe that $\Theta$ is a set of level sets that divide the simplex, and not a function.\raft{Careful: $\Theta$ does not need to divide anything; $\Theta = \{\emptyset\}$ is technically an unlabeled (degenerate) property}

\begin{definition}
Let $\Gamma:\P\toto\R$.
Define $\text{strip}(\Gamma) := \{ \Gamma_r : r \in \R \}$.
\end{definition}
Informally, strip removes labels from the property.
\jessie{Note: Strip includes the boundaries of level sets / lower dimensional level sets.}

@@

\begin{notation}
  Consider two labeled properties $\Gamma' : \P \toto \R$ and $\Gamma : \P \toto \R$.
  We say $\Gamma' \preceq \Gamma$ if removing reports from $\Gamma$ yields $\Gamma'$, that is, if $\Gamma' = \Gamma \cap \R'$ for some $\R' \subseteq \R$.
  \raft{Let's use $\preceq$ instead of $\leq$, since it's clearly different from the usual $\leq$, and easier to find--replace later.}
\end{notation}

@@

\begin{definition}\label{def:unlabeled-nonredundant}
  An elicitable, unlabeled property $\Theta$ is \emph{nonredundant} if for any full dimensional $\theta_1, \theta_2 \in \Theta$ we observe $\theta_1 \cap \theta_2 = \emptyset$ almost everywhere.
  \raft{Have not defined elicitability for unlabeled properties.  Also, what does ``almost everywhere'' mean in this context, since $\That$ is just a set of sets?  I think we just want to say that there are no distinct $\theta_1,\theta_2 \in \Theta$ such that $\theta_1 \subseteq \theta_2$.}
  \jessie{Should be equivalent to definition of nonredundancy for labeled property $\Gamma$, shown in Lemma~\ref{lem:nonredundant-defs-equivalent}.}
\end{definition}

Other notes before starting:
\begin{itemize}
\item (Assuming the metric space is $(\Delta(\Y), \rho)$, where $\rho$ is Euclidean distance, although I don't think the choice of metric matters?).
We just use this looking at interiors of level sets.
\item Using generalized Lebesgue measure on $\P \subset \reals^{|\Delta(\Y)|-1}$
\item The interior of a level set $X_r$ is defined as $\inter{X_r} = \{p \in X_r: \epsilon > 0,  \forall q \in B(\epsilon,p), r \in \argmin_r \E_q L(r,Y)\}$
\item Define the boundary of the closed set $X$ by $bd(X) := X \setminus \inter{X}$.
\item A level set $\theta$ is \emph{full-dimensional} if $dim(\aff(\theta)) = dim(P)$. 
Equivalently, $\theta$ is full-dimensional if there are distributions $p_1, p_2, \ldots, p_n \in \theta$ so that $p_1, \ldots, p_n$ are affinely independent.\raft{Careful; I think you need convexity here.  Probably you want to define full-dimensional as having nonempty interior, and prove this as a consequence of convexity.}
\item A full-dimensional level set has non-empty interior.
\end{itemize}

@@

\begin{conjecture}\label{conj:gam-prime-exists}
	Let $\Gamma$ be a nondegenerate elicitable property with a finite set of \jessie{full-dimensional} level sets \jessie{$\Theta$ so that $\bigcup_{\theta \in \Theta}\theta = \P$}.
	There exists a nondegenerate, nonredundant property $\Gamma'$ such that $\Gamma' \leq \Gamma$. 
\end{conjecture}
\begin{proof}
\emph{Assumptions used: Finite level sets, elicitability implies convex BR, i.e. differentiable a.e.}\raft{Confused by BR}
